---
title: "Event Recorder"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    #theme: darkly
    #css: "css/style.css"
    #highlight: espresso
    #ace_theme: idle_fingers
runtime: shiny_prerendered

---

```{css, echo=FALSE}
.btn-success{
  background-color: #FF9F98;
}


.alert.alert-success, .alert.alert-danger{
  background-color: #acd4a1;
  color: black;
  }
}
```




```{r setup, include=FALSE}

library(learnr)
library(gradethis)
gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)



#Event Recorder Reference:
#https://stackoverflow.com/questions/51778262/how-can-i-record-exercise-submission-in-a-learnr-r-tutorial

new_recorder <- function(tutorial_id, tutorial_version, user_id, event, data) {
    cat("-------event received----\n")
    cat(tutorial_id, " (", tutorial_version, "): ", user_id, ", ", event, "\n", data$label, ", ", data$answers, ", ", data$correct, ",\n", sep = "")
    print (data)
    cat("-------end event ---\n\n-")
    # process data here
}
options(tutorial.event_recorder = new_recorder)


#options(tutorial.event_recorder = learnr:::debug_event_recorder)
```





```{r context="server", echo = FALSE}
learnrhash::encoder_logic()
```


## Details

```{r details}
question_text(
  "Student Name:",
  answer(NULL, correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)


## Fixed-response questions

```{r planets}
question(
  "Which planet do we live on?",
  answer("Mars",   correct = FALSE),
  answer("Earth",  correct = TRUE),
  answer("Saturn", correct = FALSE),
  allow_retry = TRUE
)
```

## Multiple-response questions

```{r not_a_planets}
question(
  "Which of the following are planets?",
  answer("Mars",   correct = TRUE),
  answer("Earth",  correct = TRUE),
  answer("Saturn", correct = TRUE),
  answer("Pluto",  correct = FALSE),
  allow_retry = TRUE
)
```

## Code

```{r code, exercise=TRUE}
1+1
```

Input an expression which evaluates to 13,245

## Code - gradethis


Examine the **iris** data set.

```{r code1, exercise=TRUE}
data("iris")
head(iris)
```

How many flowers are there in the Iris dataset?

```{r nrow_iris, exercise=TRUE, exercise.reveal_solution = TRUE}
___ (iris)
```

```{r nrow_iris-hint, evaluate = FALSE}
Each observation is represented in one row. 

Can you remember which function we use to calculate the number of rows?
```

```{r nrow_iris-solution, evaluate = FALSE}
nrow(iris)
```

```{r nrow_iris-check}
#Ref: https://rdrr.io/github/rstudio-education/gradethis/man/grade_this.html

grade_this({
  # custom checking code appears here
  #print(.result)
  #print(typeof(.result))
  #print(typeof(nrow(iris)))
  if (identical(as.integer(.result), .solution)) {
    pass("There are 150 observations, i.e. 150 flowers in the dataset.")
  }
  else if (identical(.result, 5)){
    pass("Each observation is represented in one row. Did you calculate the number of columns instead of rows?")
  }
  fail("Try again!")
})



```

## Submit

```{r encoder, echo=FALSE}
learnrhash::encoder_ui()
```


<br/><br/><br/>

```{r context='server', echo=FALSE}
learnrhash::decoder_logic()
```

```{r decoder, echo=FALSE}
learnrhash::decoder_ui()
```


## Check State

```{r context="server"}
shiny::observeEvent(
  input$get_state, 
  {
    #cat(learnr:::get_tutorial_state())
    state = learnr:::get_tutorial_state()
    #print(typeof(state))
    #print(typeof(state[0]))
    #print(state[0])
    
    output$state1 = shiny::renderText(
          learnrhash:::obj_to_text(state)
    )
    
    output$state2 = shiny::renderText(
      paste(
        capture.output(str(state)),
        collapse = "\n"
      )
    )
    invisible()
  }
)
```

```{r state, echo=FALSE}
shiny::actionButton("get_state", "Get State")
shiny::br()
shiny::br()
learnrhash:::wrapped_verbatim_text_output("state1")
learnrhash:::wrapped_verbatim_text_output("state2")
```

